Conflict-Free Vertex Coloring of Planar Graphs

### 2017-04-14 presentation/presentation.tex
Working on more slides

    \begin{columns}
      \begin{column}{0.33333\textwidth}
        \only<2>{
          \begin{figure}[h]
            \centering
            \includegraphics[width=3cm]{../figures/examples-1-incorrect-1.pdf}
          \end{figure}
        }

        \only<3-7>{
          \begin{figure}[h]
            \centering
            \includegraphics[width=3cm]{../figures/examples-1-incorrect-1-corrected.pdf}
          \end{figure}
        }

        \centering
        Vertex 1 does not have a unique color in its neighborhood.
      \end{column}

@@

      \begin{column}{0.33333\textwidth}

        \only<4>{
        \begin{figure}[h]
          \centering
          \includegraphics[width=3cm]{../figures/examples-1-incorrect-2.pdf}
        \end{figure}
        }

        \only<5-7>{
        \begin{figure}[h]
          \centering
          \includegraphics[width=3cm]{../figures/examples-1-incorrect-2-corrected.pdf}
        \end{figure}
        }

        \centering
        Vertices $\{2, 3, 4\}$ do not have a unique color in their neighborhoods.
      \end{column}

@@

      \begin{column}{0.33333\textwidth}

        \only<6>{
        \begin{figure}[h]
          \centering
          \includegraphics[width=3cm]{../figures/examples-1-incorrect-3.pdf}
        \end{figure}
        }

        \only<7>{
        \begin{figure}[h]
          \centering
          \includegraphics[width=3cm]{../figures/examples-1-incorrect-3-corrected.pdf}
        \end{figure}
        }

        \centering
        Vertex 3 does not have a unique color in its neighborhood.
      \end{column}
    \end{columns}

@@

  \begin{frame}
    \frametitle{Wireless Networks}

    \begin{itemize}
      \item \textbf{Wireless networks} such as cellular networks, television broadcasts, and satellite communication systems can all benefit from conflict-free coloring.

@@

      \item A \textbf{cellular network} is a heterogeneous network with two types of nodes.

      \begin{itemize}
        \item Base-stations act as servers and are interconnected by an external backbone network.
        \pause
        \item Clients connect to base-stations via radio links. They constantly search for base-stations with strong reception.
      \end{itemize}
    \end{itemize}

@@

    \begin{itemize}
      \item The problem when designing cellular networks: \textbf{frequency assignment}.
      \begin{itemize}
        \item Imagine two nearby base-stations having the same frequency.
        \item A client in range of both base-stations would receive mutual interference.
      \end{itemize}
    \end{itemize}

    \pause
    \vspace{-0.2cm}

    \begin{itemize}
      \item This leads us to our goal: Assign frequencies such that:
      \pause
      \begin{itemize}
        \item[(1)] Every client is served by a base-station with a unique frequency.
        \pause
        \item[(2)] Minimize the number of frequencies used.
      \end{itemize}
    \end{itemize}

    \begin{figure}[h]
      \centering
      \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/towers.pdf}
      \caption*{Vertex coloring and conflict-free coloring of cellular towers, respectively}
    \end{figure}

@@

    It is wasteful to spend time coloring a graph that cannot be conflict-free colored within a certain amount of colors ($k$). Thus researchers came up with a criterion to guarantee a graph can be colored with $k$ colors.

    A \textbf{complete graph} is a graph where every pair of distinct vertices is connected by an edge.

@@

    \begin{itemize}
      \item $K_n$: A complete graph of $n$ vertices.
      \pause
      \item $K_n^{-3}$: A complete graph of $n$ vertices with any three edges forming a triangle removed.
    \end{itemize}

    \begin{theorem}
    Let $G$ be a graph and $k \geq 1$. If $G$ has neither $K_{k+2}$ nor $K_{k+3}^{-3}$ as a minor, $G$ has a conflict-free coloring that can be found in polynomial time.
    \end{theorem}

@@

@@

    \begin{textblock*}{14cm}(1cm, 7.1cm) % {block width} (coords)
      To be conflict-free colored with 1 color, graph $G$ cannot contain $K_3$ or $K_4^{-3}$ as a minor. A graph is a \textbf{minor} if it can be formed by deleting and/or contracting edges from its parent graph. \only<3>{$G$ contains both $K_3$ and $K_4^{-3}$ as a minor and thus {\color{red}\textbf{cannot}} be conflict-free colored with 1 color.}
    \end{textblock*}

>>>>

    \begin{columns}
      \begin{column}{0.33333\textwidth}
        \centering
        \vspace{4.5cm}
        Isolated vertex
        \only<2-7>{
          \begin{textblock*}{\examplewidth/3}(0.15cm,3.5cm) % {block width} (coords)
            \centering
            \includegraphics[width=3cm]{../figures/examples-1-incorrect-1.pdf}
          \end{textblock*}
        }

        \only<3-7>{
          \begin{textblock*}{\examplewidth/3}(0.15cm,6.7cm) % {block width} (coords)
            \centering
            \includegraphics[width=3cm]{../figures/examples-1-incorrect-1-corrected.pdf}
          \end{textblock*}
        }

      \end{column}

@@

      \begin{column}{0.33333\textwidth}
        \centering
        \vspace{4.5cm}
        Triangle

        \only<4-7>{
          \begin{textblock*}{\examplewidth/3}(\examplewidth/3,3.5cm) % {block width} (coords)
            \centering
            \includegraphics[width=3cm]{../figures/examples-1-incorrect-2.pdf}
          \end{textblock*}
        }

        \only<5-7>{
          \begin{textblock*}{\examplewidth/3}(\examplewidth/3,6.7cm) % {block width} (coords)
            \centering
            \includegraphics[width=3cm]{../figures/examples-1-incorrect-2-corrected.pdf}
          \end{textblock*}
        }

      \end{column}

@@

      \begin{column}{0.33333\textwidth}
        \centering
        \vspace{4.5cm}
        Missing unique

        \only<6-7>{
          \begin{textblock*}{\examplewidth/3}(10.57cm,3.5cm) % {block width} (coords)
            \centering
            \includegraphics[width=3cm]{../figures/examples-1-incorrect-3.pdf}
          \end{textblock*}
        }

        \only<7>{
          \begin{textblock*}{\examplewidth/3}(10.57cm,6.7cm) % {block width} (coords)
            \centering
            \includegraphics[width=3cm]{../figures/examples-1-incorrect-3-corrected.pdf}
          \end{textblock*}
        }
      \end{column}
    \end{columns}

@@

  \begin{frame}
    \frametitle{Applications}

    \begin{itemize}
      \item \textbf{Applications}: wireless networks, satellite communication systems, RFID networks.

@@

      \item \textbf{Cellular networks}: consist of base-stations and clients.
      \pause
      \item The problem: \textbf{frequency assignment}.

    \end{itemize}

@@

    \only<1>{
      \begin{figure}[h]
        \centering
        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/towers-slides-2.pdf}
      \end{figure}
    }

    \only<2->{
      \begin{figure}[h]
        \centering
        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/towers-slides-3.pdf}
      \end{figure}
    }

    \begin{itemize}
      \item Our goal is to assign frequencies such that:
      \pause
      \begin{itemize}
        \item[(1)] Every client is served by a base-station with a unique frequency.
        \pause
        \item[(2)] Minimize the number of frequencies used.
      \end{itemize}
    \end{itemize}

    \begin{figure}[h]
      \centering
      \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/towers-graph.pdf}
    \end{figure}

    \begin{figure}[h]
      \centering
      \includegraphics[width=10cm,trim=4 4 4 4,clip]{../figures/towers.pdf}
      \caption*{Vertex coloring and conflict-free coloring of cellular towers, respectively}
    \end{figure}

@@

    We want to guarantee a graph can be colored with $k$ colors.

@@

    \only<1-2>{
      \begin{figure}[h]
        \centering
        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion-1.pdf}
        \caption*{Graphs $K_3$ and $K_4$, respectively}
      \end{figure}
    }

    \only<3>{
      \begin{figure}[h]
        \centering
        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion-2.pdf}
        \caption*{Graphs $K_3$ and $K_4$, respectively}
      \end{figure}
    }

    \only<4>{
      \begin{figure}[h]
        \centering
        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion.pdf}
        \caption*{Graphs $K_3$ and $K_4$, respectively}
      \end{figure}
    }

    \begin{itemize}
      \item \textbf{Complete graph}: every pair of distinct vertices is connected by an edge.
      \vfill
      \pause
      \item \textbf{Tattered graph}: complete graph with a triangle removed.
    \end{itemize}

@@

  % \begin{theorem}
  % Let $G$ be a graph and $k \geq 1$. If $G$ has neither $K_{k+2}$ nor $K_{k+3}^{-3}$ as a minor, $G$ has a conflict-free coloring that can be found in polynomial time.
  % \end{theorem}

@@

    \begin{textblock*}{14cm}(1cm, 7.1cm) % {block width} (coords)
      A graph is a \textbf{minor} if it can be formed by deleting and/or contracting edges from its parent graph. To be conflict-free colored with 1 color, graph $G$ cannot contain $K_3$ or $K_4^{-3}$ as a minor.  \only<3>{$G$ contains both $K_3$ and $K_4^{-3}$ as a minor and thus {\color{red}\textbf{cannot}} be conflict-free colored with 1 color.}
    \end{textblock*}
